User-level Grid Monitoring with Inca 2

### 2007-02-23 papers/hpdc-gmw-2007/kate.tex
tg revisions
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6546 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

Inca has been deployed on TeraGrid since 2003 to validate and verify 
its Common TeraGrid Software and Services (CTSS).  TeraGrid's common user 
environment, supplied via the deployment and monitoring of CTSS, is 
designed to allow users to more easily run Grid jobs across TeraGrid's 
distributed, heterogeneous resources.

In 2006, TeraGrid added reporters to collect job usage 
information from Globus 2 GRAM logs and to detect expired host and CA 
certificates and CA CRLs to its Inca deployment.

@@

In 2006, TeraGrid's Inca deployment transitioned over to Inca 2  
and was deployed on 21 resources.   Each resource regularly executed 
an average of 109 reporters to perform 48 cross-site, 20 grid, 
28 cluster, 9 data, 2 user tool, and 2 security tests.

>>>>

TeraGrid's Coordinated TeraGrid Software and Services (CTSS)
was designed to allow users to more easily run Grid jobs across its 
distributed, heterogeneous resources.  CTSS is available 
from all TeraGrid compute resources and is comprised of approximately 30 
software packages for Grid services (gridftp, ws gram), Grid jobs (gridshell, myproxy, globus), 
cluster tools (pacman, tgusage), data management (srb, hdf5) and 
user applications (mpich, gcc).

In order to validate and verify CTSS functionality from a user perspective, TeraGrid and SDSC 
developed and deployed Inca 1 on TeraGrid in 2003. TeraGrid transitioned to Inca 2 
in 2006 and, in addition to CTSS monitoring, began using Inca to collect job usage 
information from Globus 2 GRAM logs and to detect expired host and CA 
certificates and CA CRLs to its Inca deployment.

@@

TeraGrid's Inca 2 agent, depot and consumer components are hosted at SDSC on sapa.sdsc.edu, 
a XX machine.  A reporter repository for TeraGrid is also hosted at SDSC 
on login-linux.sdsc.edu, a XX machine.  TeraGrid's 20 compute resources each 
run a reporter manager and regularly execute
an average of 109 reporters to perform 48 cross-site, 20 grid, 
28 cluster, 9 data, 2 user tool, and 2 security tests.
